---
title: "STAT/MATH 495: Problem Set 05"
author: "Luke Haggerty"
date: "2017-10-11"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
    df_print: kable
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.width=8, fig.height=4.5, message=FALSE, warning = FALSE
  )
set.seed(76)

# Load packages
library(tidyverse)
library(car)

# Note the relative file path, and not absolute file path:
train <- read_csv("data/train.csv")
test <- read_csv("data/test.csv")
sample_submission <- read_csv("data/sampleSubmission.csv")
```


# Collaboration

Please indicate who you collaborated with on this assignment: I worked individually.


# Exploratory Data Analysis

Information on the competition can be found [here](https://www.kaggle.com/c/bike-sharing-demand).

Here I use the cor() function to examine the individual corelations between count and each predictor variable. The variables with the highest corelations to count are temp, atemp, and humidity.
```{r}
cor(train$count, train$season)
cor(train$count, train$holiday)
cor(train$count, train$workingday)
cor(train$count, train$weather)
cor(train$count, train$temp)
cor(train$count, train$atemp)
cor(train$count, train$humidity)
cor(train$count, train$windspeed)
```

Using the variables with the highest corelations to count, I fit a linear model. However, I use the vif() function in the car package to examine the VIF, or Variance Inflation Factor of the variables in the model. The rule of thumb is that a VIF of 5 or greater means that the variable has too much multicollinearity with another variable in the model. This means that the inclusion of the variable(s) in my model are redundant. With the first model, using temp, atemp, and humidity, both temp and atemp have very high VIF's. This seems logical to me, as temperature (temp) and the "feels like" temperature (atemp) will be very closely related. So I fit a new model, replacing the temp variable with the variable with the next highest corelation to count, windspeed. The VIF's of the variables in the new model seem fine.
```{r}
model1 <- lm(count ~ temp + atemp + humidity, data = train)
vif(model1)

model2 <- lm(count ~ windspeed + atemp + humidity, data = train)
vif(model2)


```


# Model Fit
Here I fit the second model to the test data. I rename .fitted to count for the submission set.
```{r}
model_fit <- model2 %>% 
    broom::augment(newdata=test)

model_fit <- rename(model_fit, count = .fitted)
```


# Create Submission File
I create a dataset with only the datetime variable and the count variable from the fitted model on the test set.
```{r}
submission <- dplyr::select(model_fit, datetime, count)
write.csv(submission, "submission.csv")
```
